Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2023-12-06 article.tex
Some notes

%* list of methods for coalescing/allocating:
%   * ocamlgraph builtin
%   * greedy 
%   * briggs
%   * george
%   * welsh-powell?
\section{Graph Coloring}
The graph coloring by simplification as introduced in the Appel text takes an iterative approach.

@@

>>>>

%* list of methods for coalescing/allocating:
%   * ocamlgraph builtin
%   * greedy 
%   * briggs
%   * george
%   * welsh-powell?
\section{Graph Coloring}
The heuristic for graph coloring as introduced in both the Appel and Aho et al. texts is a linear time approximation of an NP-complete problem. It is based on an iterative approach.

Let \(k\) be the number of working registers available on the target architecture. After building the interference graph \(G\), a node \(n\) with fewer than \(k\) neighbors is chosen. As \(n\) has at most \(k-1\) neighbors, it can be removed safely by ensuring it is not assigned any color assigned to its neighbors, effectively simplifying \(G\).

%  (i.e. \(\mathit{deg}(n) < k\))

It must hold that \(G-\{n\}\) is \(k\)-colorable if \(G\) is \(k\)-colorable

@@

%% NOTE: special implementations
%%
%% * phi nodes
%% * calling convention:
%%   * save/restore callee saved registers in pro/epilogue
%%   * save/restore caller saved registersk before call
%% * jump flags for comparison
